\ttitle

### 2013-12-19 Chapters/Chapter5.tex
WIP: Finalizing chapter 3
WIP: chapter 4
FrontmatteR

\lhead{Chapter 5. \emph{Artificial data results}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
\section{Outline}
\emph{Not intented for the reader.}
\begin{itemize}
  \item Compare proposed method with methods of \Cref{Chapter2}
  \item Provide KL-analysis (as Takeuchi does)
  \item Provide plots, tables, graphs, error rates, precision, etc.
  \item Apply to a multiple of data, to compare to previous research - use that data
  \item Give theoretical analysis about performance. Big-O, memory, run-time, precision.
  \item This sections needs programmed implementations of own method and the ones compared
\end{itemize}

In this chapter we will apply the proposed algorithm to artificial data sets.
For comparison, we use some of the data sets that are used by Camci~\cite{camci2010change} and Takeuchi \etal \cite{takeuchi2006unifying}.
These data sets are generated by Gaussian noise distributions.
In \Cref{sec:artificial_data_generation} the precise generation method and characteristics of the data sets are discussed.
For our final change detection mechanism we use the \gls{rt}-method, also applied by Camci \cite{camci2010change}.
This is a simple and fast method and allows us to mainly focus on the \gls{oc-svm} model properties that should reflect changes in the data.
The results of these two methods are discussed in \Cref{sec:artificial_data_results}.

@@

>>>>

\lhead{Chapter 5. \emph{Artificial data results}} % This is for the header on each page - perhaps a shortened title
\begin{itemize}
  \item Problemen met SVM methode: ook na de verandering blijft de threshold nog stijgen;
  \item Veranderingen in mean geven ``extra'' change point wanneer alle data weer in het window zit. Zie \Cref{fig:camci_fixed_increasing_mean} op de 50-tallen.
\end{itemize}

In this chapter we will apply the proposed algorithm as stated in the previous chapter to artificial data sets.
For comparison, we use some of the data sets that are used by Camci~\cite{camci2010change} and Takeuchi and Yamanishi~\cite{takeuchi2006unifying}.
These data sets are generated by Gaussian noise distributions.
In \Cref{sec:artificial_data_generation} the precise generation method and characteristics of the data sets are discussed.
For our final change detection mechanism we use the \gls{rt}-method, also applied by Camci \cite{camci2010change}.
This is a simple and fast method and allows us to mainly focus on the \gls{oc-svm} model properties that should reflect changes in the data.
The results of these two methods are discussed in \Cref{sec:artificial_data_results}.

@@

\TODO{Add short section on quality metrics}

### 2013-12-19 Chapters/Chapter5/artificial_data_generation.tex
FrontmatteR

  \item \textbf{Reduced increasing mean:} at each change point $y$ the mean is increased with $\Delta(y) = 10 - y$.
  This set origins as the first data set of Takeuchi \etal \cite{takeuchi2006unifying}.
  In contrast with the previous set, in this set the absolute difference in mean is reduced over time.
  The data is plotted in \Cref{fig:takeuchi_reduced_increasing_mean}.

@@

  \item \textbf{Alternating variance:} at each change point $y$ the variance $\sigma^2$ is set to $9.0$ when $y$ is odd, and to $1.0$ otherwise.
  This set origins as the thirds sets from Camci~\cite{camci2010change} and Takeuchi \etal \cite{takeuchi2006unifying}.
  This data set is used to measure the ability of detecting changes in decrease of variance, as Camci~\cite{camci2010change} claims is not trivial.
  The data is plotted in \Cref{fig:camci_takeuchi_alternating_variance}.
\end{enumerate}

>>>>

  \item \textbf{Reduced increasing mean:} at each change point $y$ the mean is increased with $\Delta(y) = 10 - y$.
  This set origins as the first data set of Takeuchi and Yamanishi~\cite{takeuchi2006unifying}.
  In contrast with the previous set, in this set the absolute difference in mean is reduced over time.
  The data is plotted in \Cref{fig:takeuchi_reduced_increasing_mean}.

@@

  \item \textbf{Alternating variance:} at each change point $y$ the variance $\sigma^2$ is set to $9.0$ when $y$ is odd, and to $1.0$ otherwise.
  This set origins as the thirds sets from Camci~\cite{camci2010change} and Takeuchi and Yamanishi~\cite{takeuchi2006unifying}.
  This data set is used to measure the ability of detecting changes in decrease of variance, as Camci~\cite{camci2010change} claims is not trivial.
  The data is plotted in \Cref{fig:camci_takeuchi_alternating_variance}.
\end{enumerate}

### 2013-12-19 Chapters/Chapter5/results.tex
FrontmatteR

% !TEX root = ../../main.tex
\section{Results}\label{sec:artificial_data_results}
For an objective measure of quality of the proposed method applied to the four aforementioned data sets, we employ two metrics, as defined by Takeuchi \etal \cite{takeuchi2006unifying}.
The first metric is the $\operatorname*{average \_ benefit}$, for which we first need to define the notion of $\operatorname*{benefit}$ for each change:
\begin{equation}\label{eq:benefit}
  \operatorname*{benefit}(y) = 1 - |t_y - t_y^*| / 10  \mbox{~~~(when } |t_y - t_y^*| < 10 \mbox{)},
\end{equation}
where $t_y$ is the time of the discovered change point and $t_y^*$ is the true change time.
We can then define the $\operatorname*{average \_ benefit}$ over all the discovered change points $Y$ as:
\begin{equation}\label{eq:average_benefit}
  \operatorname*{average \_ benefit}(Y) = \frac{\sum_{y=1}^Y \operatorname*{benefit}(y)}{Y}.
\end{equation}
Besides the benefit, which rewards discovered change points close to the actual change points, we need to penalize discovered change points which do not relate to a true change point.
For this we use the \acrlong{far}, expressed as
\begin{equation}\label{eq:false_alarm_rate}
  \operatorname*{far}(Y) = \frac{Y_{\operatorname*{false}}}{Y}.
\end{equation}

>>>>

% !TEX root = ../../main.tex
\section{Results}\label{sec:artificial_data_results}
For an objective measure of quality of the proposed method applied to the four aforementioned data sets, we employ two metrics, as defined by Takeuchi and Yamanishi~\cite{takeuchi2006unifying}.
The first metric is the $\operatorname*{average \_ benefit}$, for which we first need to define the notion of $\operatorname*{benefit}$ for each change:
\begin{equation}\label{eq:benefit}
  \operatorname*{benefit}(y) = 1 - |t_y - t_y^*| / 10  \mbox{~~~(when } |t_y - t_y^*| < 10 \mbox{)},
\end{equation}
where $t_y$ is the time of the discovered change point and $t_y^*$ is the true change time.
We can then define the $\operatorname*{average \_ benefit}$ over all the discovered change points $Y$ as:
\begin{equation}\label{eq:average_benefit}
  \operatorname*{average \_ benefit}(Y) = \frac{\sum_{y=1}^Y \operatorname*{benefit}(y)}{Y}.
\end{equation}
Besides the benefit, which rewards discovered change points close to the actual change points, we need to penalize discovered change points which do not relate to a true change point.
For this we use the \acrlong{far}, expressed as
\begin{equation}\label{eq:false_alarm_rate}
  \operatorname*{far}(Y) = \frac{Y_{\operatorname*{false}}}{Y}.
\end{equation}

### 2013-12-19 main.tex
wip
Add paper to Appendix C
WIP
Add quotes on performance of SVMs
WIP: chapter 4, description of experiment methods
Added the TODO command
Prefix refs with non-breaking space and capitalize refs
Add caption titles to tables
Restructure Chapter 5 graphs of data sets
WIP: Introduction
Put stills in grid. Crop images
WIP: Chapter 4
FrontmatteR

\usepackage[square, numbers, comma, sort&compress]{natbib} % Use the natbib
%reference package - read up on this to edit the reference style; if you want
%text (e.g. Smith et al., 2012) for the in-text references (instead of
%numbers), remove 'numbers'
\usepackage{isomath}
\usepackage{paralist}
\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue -
%change to black if annoying
\title{\ttitle} % Defines the thesis title - don't touch this

@@

\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

@@

@@

@@

\textsc{\LARGE \univname}\\[1.5cm] % University name
\textsc{\Large Doctoral Thesis}\\[0.5cm] % Thesis type

@@

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{http://www.johnsmith.com}{\authornames} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{http://www.jamessmith.com}{\supname} % Supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[3cm]

\large \textit{A thesis submitted in fulfilment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
\textit{in the}\\[0.4cm]
\groupname\\\deptname\\[2cm] % Research group name and department name

@@

\textit{``Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism."}

\begin{flushright}
Dave Barry
\end{flushright}

@@

@@

@@

\lhead{\emph{Symbols}} % Set the left side page header to "Symbols"

\listofnomenclature{lll} % Include a list of Symbols (a three column table)
{
$a$ & distance & m \\
$P$ & power & W (Js$^{-1}$) \\
% Symbol & Name & Unit \\

& & \\ % Gap to separate the Roman symbols from the Greek

$\omega$ & angular frequency & rads$^{-1}$ \\
% Symbol & Name & Unit \\
}

@@

\clearpage
\setstretch{1.3} % Return the line spacing back to 1.3

\pagestyle{empty} % Page style needs to be empty for this page

\dedicatory{For/Dedicated to/To my\ldots} % Dedication text

@@

\input{./Appendices/AppendixA-Summaries}
\input{./Appendices/AppendixB-Camci}
%\input{./Appendices/AppendixB}
%\input{./Appendices/AppendixC}

@@

\bibliographystyle{unsrtnat} % Use the "unsrtnat" BibTeX style for formatting the Bibliography

>>>>

\usepackage[square, numbers, comma, sort&compress]{natbib} % Use the natbib
%reference package - read up on this to edit the reference style; if you want
%text (e.g. Smith et al., 2012) for the in-text references (instead of
%numbers), remove 'numbers'
\usepackage{isomath}
\usepackage{paralist}
\usepackage{tabulary}
\usepackage{cleveref}
\usepackage{subcaption}
\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue -
%change to black if annoying
\title{\ttitle} % Defines the thesis title - don't touch this

@@

\DeclareMathOperator*{\argminold}{\arg\!\min}
\DeclareMathOperator*{\argmaxold}{\arg\!\max}

@@

\usepackage{templates/math_shorthands}

@@

\newcommand{\TODO}[1]{\emph{\textbf{*** TODO: {#1} ***}}}

@@

\textsc{\LARGE \univname}\\[1.5cm] % University name
\textsc{\Large Master's Degree Thesis}\\[0.5cm] % Thesis type

@@

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{http://rvlasveld.github.io}{\authornames}, \href{http://www.uu.nl}\textsc{UU} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushright} \large
\emph{Supervisors:} \\
\href{http://www.cs.uu.nl/staff/gv.html}{Dr. G.A.W. \textsc{Vreeswijk}, \href{http://www.uu.nl}\textsc{UU}}  \\ % Supervisor name - remove the \href bracket to remove the link
\href{http://www.annevanrossum.com}{Anne \textsc{van Rossum}, \href{http://www.almende.com}\textsc{Almende B.V.}} % Supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[3cm]

\large \textit{A thesis submitted in fulfilment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
\textit{in the}\\[0.4cm]
\facname\\\deptname\\[2cm] % Research group name and department name

@@

\textit{``All truly great thoughts are conceived by walking."}

\begin{flushright}
Friedrich Nietzsche
\end{flushright}

@@

\TODO{Write abstract}

@@

\glsresetall

@@

% \lhead{\emph{Symbols}} % Set the left side page header to "Symbols"

% \listofnomenclature{lll} % Include a list of Symbols (a three column table)
% {
% $a$ & distance & m \\
% $P$ & power & W (Js$^{-1}$) \\
% % Symbol & Name & Unit \\

% & & \\ % Gap to separate the Roman symbols from the Greek

% $\omega$ & angular frequency & rads$^{-1}$ \\
% % Symbol & Name & Unit \\
% }

@@

% \clearpage
% \setstretch{1.3} % Return the line spacing back to 1.3

% \pagestyle{empty} % Page style needs to be empty for this page

% \dedicatory{For/Dedicated to/To my\ldots} % Dedication text

% \addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

@@

% \input{./Appendices/AppendixA-Summaries}
% \input{./Appendices/AppendixB-Camci}
% \input{./Appendices/AppendixC}
% \input{./Appendices/AppendixD-Planning}
% \input{./Appendices/AppendixE-Data-structure}
% \input{./Appendices/AppendixF-final}

@@

% \bibliographystyle{unsrtnat} % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliographystyle{plainnat} % Use the "unsrtnat" BibTeX style for formatting the Bibliography
